---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# roam.demo

<!-- badges: start -->
<!-- badges: end -->

The goal of roam.demo is to demonstrate the use of [`roam`](https://github.com/FinYang/roam) in a package.

This package contains two (remote) dataset. 

- `bee`: Bee colony data from the 2022-01-11 [TidyTuesday project](https://github.com/rfordatascience/tidytuesday).
- `tidytuesday2026Jan`: Versioned data from 2026-01-13 and 2026-01-20 [TidyTuesday project](https://github.com/rfordatascience/tidytuesday)
    - Includes versions `2026-01-13` and `2026-01-20`

## Installation

You can install the development version of roam.demo like so:

``` r
# install.packages("remotes")
remotes::install_github("FinYang/roam.demo")
```
## Documentation

The documentation in this package is generated using `roxygen2`. For each roam object, the `format` tag must be explicitly defined. When `roxygen2` generates the *Format* section, it evaluates the object and records the structure of the resulting output. If a roam object is not cached locally, this evaluation returns `NULL`, and the documented format will incorrectly reflect a `NULL` object. As a result, the generated documentation may vary across devices depending on their local cache state. To avoid this inconsistency, the `format` tag should always be explicitly specified for roam objects.

## Example


```{r example}
library(roam.demo)
options(roam.autodownload = TRUE)

head(bee)
```



```{r}
head(tidytuesday2026Jan)

invisible(roam_install(tidytuesday2026Jan, version = "2026-01-13"))
head(tidytuesday2026Jan)
```
